---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rd2list

`rd2list` is a package for extracting R documentation into a structured, 
human-readable list.  Use this package if you've ever wanted to get the help text for a function as a string.

* `get_doc()` - get a structured, human-readable list of the documentation for a function.
* `get_rd_doc()` - fetch the Rd object for a function from an installed package.
* `rd2list()` - parse an Rd object into a structured, human-readable list.

## Installation

You can install from github with:

``` r
remotes::install_github("coolbutuseless/rd2list")
```

## Example - Getting documentation as a list

```{r example}
doc <- rd2list::get_doc(function_name = 'geom_path', package = 'ggplot2')

doc$title
```


```{r eval = FALSE}
doc$description
```

```{r echo = FALSE, width = 10}
# Jumping through some hoops. must be an easier way...
cat(paste(strwrap(doc$description), collapse="\n"))
```


```{r}
doc$arguments$linejoin
```



```{r}
doc$alias
```


## Example - Getting documentation as an Rd object

The raw Rd documentation object can be fetched using `get_rd_doc()`.

```{r eval = FALSE}
rd2list::get_rd_doc(function_name = 'diag', package_name = 'base')
```

```{r eval = FALSE}
$title
$title[[1]]
[1] "Matrix Diagonals"
attr(,"Rd_tag")
[1] "TEXT"

attr(,"Rd_tag")
[1] "\\title"

$name
$name[[1]]
[1] "diag"
attr(,"Rd_tag")
[1] "VERB"

attr(,"Rd_tag")
[1] "\\name"

$alias
$alias[[1]]
[1] "diag"
attr(,"Rd_tag")
[1] "VERB"

attr(,"Rd_tag")
[1] "\\alias"

[... output trimmed]
```





# Related documents and packages:

* [Rd parsing](https://developer.r-project.org/parseRd.pdf) - developer documentation
  for parsing and understanding the `Rd` format.
* [Rd2md](https://cran.r-project.org/package=Rd2md) converts Rd documentation to 
  a markdown document.
* [gbRd](https://cran.r-project.org/package=gbRd) which 
  provides utilities for processing Rd objects and files.
* [Rdpack](https://cran.r-project.org/package=Rdpack) which 
  provide functions for manipulation of R documentation objects.
* [fgui](https://cran.r-project.org/package=fgui) used to offer some functionality
  for extracting document. `fgui::parseHelp()` used to work, but has been disabled by author.

